Main manuscript

### 2021-12-08 Manuscript/Manuscript.tex
add line numbers

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}
\usepackage{graphicx}

@@

\usepackage{caption}
\usepackage{placeins}
\usepackage{amsmath}
\captionsetup[table]{labelformat=empty}
\captionsetup[figure]{labelformat=empty}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

the COVID19 pandemic, thanks to decreased journals' processing time and
the diffusion of preprint databases' usage (Aviv-Reuven and Rosenfeld
2021; Horbach 2020; Hoy 2020). Consequently, it gets harder for
researchers and practitioners to stay up-to-date on the latest findings
in their field. Secondary research is of paramount relevance in this
scenario, providing valuable summaries of the latest research results,
but is getting ever more demanding in terms of time and human resources
(Allen and Olkin 1999; Borah et al. 2017; A. M. Cohen et al. 2010;
Bastian, Glasziou, and Chalmers 2010).\\

@@

(Ikonomakis, Kotsiantis, and Tampakas 2005). One of the most successful
approaches to text screening is active machine learning: researchers
review the predictions made by the learning algorithm, focusing on the
most uncertain predictions (``uncertainty'' based active machine
learning) or on those giving a document a higher probability of being
relevant (``certainty'' based active ML) (Miwa et al. 2014).\\
The automatisation of systematic reviews has been ripe with improvements
in the last years, and it is possible to foresee that such techniques
will become a standard approach (E. Beller et al. 2018). See Ananiadou
et al. (2009); O'Mara-Eves et al. (2015); Tsafnat et al. (2013);
Jonnalagadda, Goyal, and Huffman (2015) for in-depth evaluations of
research in this field. Many of these studies have generated a set of
user-friendly commercial and free-to-use tools (see Marshall and Wallace
2019, table 1). Despite the significant advances, each method has
various shortcomings, both in usability and efficiency (O'Mara-Eves et
al. 2015). We tried to address some of these limitations by creating an
integrated framework that tries to simplify systematic reviews in
innovative ways: we provide solutions for automatic citation collection
and management from multiple online sources and a Bayesian, active
machine learning-based tool to support humans in the screening task,
exponentially reducing the number of records to review. In particular,
we exploit the characteristics of Bayesian analysis to overcome the
shortcoming of both ``certainty'' and ``uncertainty'' based active
learning and the difficulties in defining stopping rules (Miwa et al.
2014). Finally, we propose an experimental method to semi-automatically
generate efficient search queries given an already labelled set of
publications.\\

@@

microorganisms. The actual protocol of this systematic review is
published in (Sadaghiani et al. 2020).\\

@@

We built an R (R Core Team 2020) based framework to simplify two aspects
of systematic reviews: record acquisition and classification. The
framework comprises several modules that communicate through
intermediate outputs stored in standard formats, which make it possible
for users to extend the framework or easily integrate it with other
tools in their pipeline. See Supplemental Material S1 for an in-depth
description of the framework and how to use it.\\
The tasks carried out by the framework are grouped into ``sessions'',
i.e., a set of actions that starts from a search query to obtain a set
of scientific citation data (records), which are then labelled as
relevant (``positive'' in the rest of the text) or not (``negative'')
for the topic of interest (Fig. 1). The framework can generate a new
query from this labelled set and perform a new session to find records
possibly missed by the first query.\\
The researcher initiates the process with a starting query derived by
domain knowledge from which she expects a high relevant/non-relevant
record ratio.\\
Follows a description of the framework's components.\\

@@

We built a set of tools to let users automatically search and download
citation data from three major scientific databases (``sources''):
Pubmed (\url{https://pubmed.ncbi.nlm.nih.gov/}), Web Of Science (WOS,
\url{https://apps.webofknowledge.com/}) and the Institute of Electrical
and Electronics Engineers (IEEE,
\url{https://ieeexplore.ieee.org/Xplore/home.jsp}). The framework takes
care of authorization management for non-open databases like WOS and
IEEE. It is also possible to download and import records in the
framework manually; this is particularly useful to acquire records from
the SCOPUS
(\url{https://www.scopus.com/search/form.uri?display=basic\#basic}) and
EMBASE databases
(\url{https://www.embase.com/\#advancedSearch/default}), for which a
comprehensive API interface was not easy to build. An extra manual
search was necessary also for Pubmed, since the API and the web
interface have different rule expansion algorithms and return slightly
different results ({`NCBI Insights : Updated Pubmed e-Utilities Coming
in April 2022!'} n.d.). A short guide on how to set up the framework for
each supported database is available in Supplemental Material S3.\\
The acquired records are merged into a single database, resolving
duplicates and different formatting between sources. The records are
ordered according to the frequency of the positive query terms (e.g.,
not preceded by a \(NOT\) modifier) in the title and abstract (``simple
query ordering'').\\
The researcher is then asked to label a number of records to create the
``initial training set'' needed to start the automatic classification.
We suggest manually labelling the first 250 records (see
``hyperparameter optimization'' later). The simple query ordering
increases the positivity rate in the initial training set (Wallace,
Small, et al. 2010), which provide higher sensitivity during automatic
classification (Chawla, Japkowicz, and Kotcz 2004).

@@

The collected citation data have a number of fields characterizing a
scientific publication. The framework models the relevance of a record
based on the following fields: title, abstract, authors, keywords, MESH
terms (Lipscomb 2000). A series of Natural Language Processing (NLP)
techniques (Baeza-Yates, Ribeiro-Neto, and others 1999; Marshall and
Wallace 2019; Ananiadou and McNaught 2006) are employed to transform the
textual information in these fields into features for machine learning
through a bag-of-words approach (Marshall and Wallace 2019). The
processing of free text fields (title, abstract) includes: tokenization
(i.e., extracting the terms), common stopwords (i.e., sentence
components bringing no meaning) removal, part-of-speech filtering (only
nouns, adjectives, verbs and untagged terms are retained), and
lemmatization of the terms (i.e., reduction to their base grammar form).
Text processing for authors, keywords and MESH terms identifies logical
units (e.g., author's full names, composite keywords) and extracts
them.\\
Terms appearing in less than 5\% of the labelled documents are removed
from negative records. All terms in the positive set are kept to
increase sensitivity at the cost of specificity.\\
Some terms tend to co-appear in records (non-consecutive ngrams,
nc-ngrams), often carrying a particular meaning when copresent. To
detect nc-ngrams, we generated a word network representation (Francois
Rousseau 2015) posing edges between terms with a cosine similarity in
terms of record co-occurrence \textgreater{} 0.5. We extracted the
maximal cliques in the network (Eppstein, Löffler, and Strash 2010)
representing highly correlated groups of terms; These groups of terms
are added to the data set as individual features. Only nc-ngrams
comprising a maximum of ten terms are kept.\\
A second network is built using a co-occurrence threshold of 0.9. In
this case, the cliques represent terms that always appear together and
therefore can be considered redundant (i.e., they do not need to be
considered separately). These terms are merged to increase computation
efficiency and reduce overfitting.\\
The output is a Document-Term Matrix (DTM), with \(N_d\) rows
representing the records (\(D_i\)), \(N_t\) terms column for the
\(t_{field}\) terms (divided by record field) and \({0,1}\) values
whether \(t_{field} \in D_i\). We also enriched the DTM with features
referencing the number of terms in each field to help the model scale
term importance based on the field length.

@@

To assign the labels, we employed an ``active learning'' Miwa et al.
(2014) approach, where a human reviews a specific subset of predictions
made from the machine, which is then retrained on the manually reviewed
dataset. This process proceeds iteratively, decreasing prediction
uncertainty.\\
Label assignment is done through the identification of an ``uncertainty
zone'' whose construction is possible thanks to the Bayesian nature of
BART, which provides full PPDs instead of point-wise predictions for
each record.\\
To describe the process formally, we define

@@

\hypertarget{relevant-terms-extraction}{%
\subsection{Relevant terms'
extraction}\label{relevant-terms-extraction}}

@@

Since the algorithm is data-driven, it creates queries that effectively
select positive records from the input dataset but may be not specific
enough once applied to actual research databases. Therefore we appended
an extra subquery in \(AND\), which specifies the general topics of our
search and delimitates the search domain.\\
The new query was used to initiate a second search session.

@@

We trained a simple Bayesian logistic regression (surrogate model) on
the reviewed records to evaluate the classification model consistency
(see Discussion for the theoretical justification). The surrogate model
uses as predictor the lower bound of the 98\% PrI of the records' PPD
with weakly regularizing, robust priors for the intercept (Student T
with \(\nu=3,\mu=0,\sigma=2.5\)) and the linear coefficient (Student T
with \(\nu=3,\mu=0,\sigma=1.5\)).\\
The quality of the model was evaluated through Bayesian \(R^2\) (Gelman
et al. 2019), of which we reported the posterior median and 90\%
Credible Interval {[}90\% CrI{]}. The \(R^2\) also provides an
evaluation of the consistency of the original classification model.
Given that this model is conditional only on the BART predictions and
not on the DTM, it is characterized by more uncertainty, providing
plausible worst-case scenarios.\\
The surrogate model is then used to generate the predictive cumulative
distribution of the number of missed positive records in the whole
dataset. This distribution allows estimating the expected total
posterior ``Sensitivity'' and the ``Work saved over random'' (WSoR) of
the classification model in the full (unreviewed) dataset. The WSoR is
one minus the number of records to manually label at random to find the
same number of positives; this last quantity is estimated through a
negative hypergeometric distribution (Chae 1993).\\
For the number of predicted positive records, the sensitivity and the
WSoR, we reported the ``truncated 90\% PrI'' {[}trunc. 90\% PrI{]},
which is the uncertainty interval bounded at the number of observed
total positive records (i.e., there cannot be less predicted positive
records than observed).

@@

To evaluate the hyperparameter effect of performance, we set up a ``grid
search'' (Claesen and De Moor 2015; L. Yang and Shami 2020) on a
prelabelled ``validation set'' made of the first 1200 records from the
first session dataset. The framework tested each hyperparameter
combination until four CR iterations with no positive records were
returned or the whole dataset got labelled.\\
For each combination, a performance score was computed as the product of
``Efficiency'' (1 minus the ratio of records that required review over
the total) and ``Sensitivity'' (number of positive records found over
the total of positives). We then identified homogeneous ``performance
clusters'' of scores given hyperparameter values using a partition tree
(Therneau and Atkinson 2019). For the rest of the study, we used the
best hyperparameter set in terms of Sensitivity followed by Efficiency
from the cluster with the highest average score.

@@

The input search query for the first session was:\\

@@

The first search session returned a total of 27600 unique records,
specifically 12719 (71.6\% of the total) records from the EMBASE
database, followed by 9546 (53.8\%) from Pubmed, 3175 (17.9\%) from
SCOPUS, 2100 (11.8\%) from WOS, and 60 (0.34\%) from IEEE (Table 1).
There were various degrees of overlapping between sources, with the
38.4\% of records being present in more than one database and EMBASE and
IEEE being the databases with the higher uniqueness ratios. The final
dataset was composed by 17755 unique records.\\
The first 250 records were manually labeled. Of these 43 (17.2\%) were
labeled as positive, and 207 (82.8\%) as negative.

@@

\caption{\label{tab:session 1}\textbf{Table 1}. Distribution of retrieved records by source and session. For each source it is reported the number of records, percentage over the session total (after removing duplicates)' and, number or records specific for a source as absolute value and as percentage over the source total. All session shows records after joining and deduplication of the Session 1 and Session 2 dataset.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrlrl}
\toprule
Session & Source & Records & \% over total & Source specific records & \% over source total\\
\midrule
\cellcolor{gray!6}{Session1} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{17755} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 12719 & 71.6\% & 6683 & 52.5\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{9546} & \cellcolor{gray!6}{53.8\%} & \cellcolor{gray!6}{3457} & \cellcolor{gray!6}{36.2\%}\\
 & Scopus & 3175 & 17.9\% & 298 & 9.39\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{2100} & \cellcolor{gray!6}{11.8\%} & \cellcolor{gray!6}{473} & \cellcolor{gray!6}{22.5\%}\\
\addlinespace
 & IEEE & 60 & 0.34\% & 29 & 48.3\%\\
\cellcolor{gray!6}{Session2} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{82579} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 48396 & 58.6\% & 40826 & 84.4\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{28811} & \cellcolor{gray!6}{34.9\%} & \cellcolor{gray!6}{18021} & \cellcolor{gray!6}{62.5\%}\\
 & Scopus & 17070 & 20.7\% & 4908 & 28.8\%\\
\addlinespace
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{12956} & \cellcolor{gray!6}{15.7\%} & \cellcolor{gray!6}{2817} & \cellcolor{gray!6}{21.7\%}\\
 & IEEE & 61 & 0.074\% & 22 & 36.1\%\\
\cellcolor{gray!6}{All Sessions} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{98371} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 59604 & 60.6\% & 46942 & 78.8\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{37278} & \cellcolor{gray!6}{37.9\%} & \cellcolor{gray!6}{21371} & \cellcolor{gray!6}{57.3\%}\\
\addlinespace
 & Scopus & 19353 & 19.7\% & 5181 & 26.8\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{14367} & \cellcolor{gray!6}{14.6\%} & \cellcolor{gray!6}{3175} & \cellcolor{gray!6}{22.1\%}\\
 & IEEE & 108 & 0.11\% & 48 & 44.4\%\\
\bottomrule
\end{tabular}}
\end{table}

@@

The ``\&'' indicates nc-ngrams, i.e., terms strongly co-occurrent in the
documents.\\
The engine was able to pick up the central concept of the research,
i.e., ``patient transport'' or ``transfer'' through a ``network'' of
``facility''ies that facilitates the ``spread'' of infections, and even
one of the authors of this study (Donker T.) or the region of interest
(``Orange County'') of another research group active on the topic of
healthcare asociated pathogen spreading over hospital networks. It is
interesting to see that some terms were considered highly relevant for
the BART models (e.g., ``Worker'' in 6th position out of more than 3800
terms considered) although in a simpler linear model their effect would
be hardly significant (statistic: -1.21 s.e.); these are terms which are
relevant only together with other terms but not by themselves,
highlighting the extra predictive power brought by a non-linear model
like BART.\\
A more extensive set of terms is presented in Table 1 of Supplemental
Material S2.

@@

\caption{\label{tab:performance}\textbf{Table 3}. Estimated performance summary. The table reports for each session, the number of reviewed records and the percentage over the total. Also, the posterior expected number of positive records, "Sensitivity" and "Work saved over random" (WSoR) are reported, with their 90\% PrI truncated to a number of positive matches equal to the observed one. Finally the median Bayesian $R^2$ [90\% CrI] of the logistic models is reported. [PrI] represents the 90\% Predictive Interval while [trunc. PrI] indicate the residual PrI truncated at the observed realization (see. methods).}
\centering
\begin{tabular}[t]{lll}
\toprule
Indicator & Session 1 & Session 2\\
\midrule
\cellcolor{gray!6}{Total records} & \cellcolor{gray!6}{17755} & \cellcolor{gray!6}{98371}\\
Reviewed records (\% over total records) & 761 (4.29\%) & 1316 (1.34\%)\\
\cellcolor{gray!6}{Expected efficiency (over random) [trunc. 90\% PrI]} & \cellcolor{gray!6}{95.7\% [95.3\%, 95.7\%]} & \cellcolor{gray!6}{98.6\% [98.2\%, 98.7\%]}\\
Observed positive matches (\% over total records) & 101 (0.57\%) & 107 (0.11\%)\\
\cellcolor{gray!6}{Predicted positive matches [trunc. 90\% PrI]} & \cellcolor{gray!6}{101 [101, 108]} & \cellcolor{gray!6}{110 [107, 145]}\\
\addlinespace
Expected sensitivity [trunc. 90\% PrI] & 100\% [93.5\%, 100\%] & 97.3\% [73.8\%, 100\%]\\
\cellcolor{gray!6}{Simple Model $R^2$ [90\% PrI]} & \cellcolor{gray!6}{98.1\% [97.4\%, 98.3\%]} & \cellcolor{gray!6}{98.2\% [97.6\%, 98.3\%]}\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx}

@@

\usepackage{caption}
\usepackage{placeins}
\usepackage{amsmath}
\usepackage{lineno}
\linenumbers
\captionsetup[table]{labelformat=empty}
\captionsetup[figure]{labelformat=empty}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

the COVID-19 pandemic, thanks to faster article' processing time by
publishers and the diffusion of preprint databases' usage (Aviv-Reuven
and Rosenfeld 2021; Horbach 2020; Hoy 2020). Consequently, it gets
harder for researchers and practitioners to stay up-to-date on the
latest findings in their field. Secondary research is of paramount
relevance in this scenario, providing valuable summaries of the latest
research results, but is getting ever more demanding in terms of time
and human resources (Allen and Olkin 1999; Borah et al. 2017; A. M.
Cohen et al. 2010; Bastian, Glasziou, and Chalmers 2010).\\

@@

(Ikonomakis, Kotsiantis, and Tampakas 2005).\\
The automation of systematic reviews has been ripe with improvements in
the last years (Ananiadou et al. 2009; O'Mara-Eves et al. 2015; Tsafnat
et al. 2013; Jonnalagadda, Goyal, and Huffman 2015), and it is possible
to foresee that it is going to become the standard approach in the field
(E. Beller et al. 2018), with many solutions already being turned into
commercial and free-to-use tools (see Marshall and Wallace 2019, table
1).\\
In this manuscript we present an open source, production-ready framework
which further contributes to the state-of-the-art in systematic review
automation (SRA) and helpers (SRH) tools. We improve the ``retrieval
phase'' by providing a unified framework for the automatic collection
and management of scientific literature from multiple online sources.
For the citation screening (appraisal) phase, we built an active machine
learning-based Miwa et al. (2014) protocol, which exploits a Bayesian
framework to efficiently identify potentially relevant documents that
require human review while automatically screening-out the large
majority of clearly non-relevant ones; the algorithm then uses human
reviews to iteratively increase classification accuracy. Finally, we
included a tool to generate new search queries given an already labelled
citation data set, in order to identify relevant research possibly
missed by human-made queries.\\

@@

microorganisms; the protocol is published in (Sadaghiani et al. 2020).\\

@@

We built an R (R Core Team 2020) based framework to simplify two aspects
of systematic reviews: record acquisition and classification. The code
used to generate the results in the manuscript is available at X while
an update version of the framework is distributed as an R package at Y.
The framework includes several modules that communicate through
intermediate outputs stored in standard formats, which make it possible
for users to extend the framework or easily integrate it with other
tools in their pipeline. See Supplemental Material S1 for an in-depth
description of the framework and how to use it.\\
The tasks carried out by the framework are grouped into ``sessions'',
which comprise obtaining scientific citation data (records) using a
search query and then labelling them as relevant (``positive'' in the
rest of the text) or not (``negative'') for the topic of interest with
the help of a machine learning engine (Fig. 1). The initial search query
should be built using domain knowledge, trying to achieve a high
relevant/non-relevant record ratio.\\
The framework can then generate a new data-driven query from this
labelled set to perform a new session to find records possibly missed by
the first query.\\

@@

We built a set of tools to let users automatically search and download
citation data from three major scientific databases (``sources''):
Pubmed (\url{https://pubmed.ncbi.nlm.nih.gov/}), Web Of Science (WOS,
\url{https://apps.webofknowledge.com/}) and the Institute of Electrical
and Electronics Engineers (IEEE,
\url{https://ieeexplore.ieee.org/Xplore/home.jsp}). The framework takes
care of authorization management for non-open databases like WOS and
IEEE. It is also possible to download and import records in the
framework manually; this is particularly useful to acquire records from
the SCOPUS (\url{https://www.scopus.com/}) and EMBASE databases
(\url{https://www.embase.com/}), for which a comprehensive API interface
was not easy to build. An extra manual search was necessary also for
Pubmed, since the API and the web interface have different rule
expansion algorithms and return slightly different results ({`NCBI
Insights : Updated Pubmed e-Utilities Coming in April 2022!'}, n.d.). A
short guide on how to set up the framework for each supported database
is available in Supplemental Material S3.\\
The acquired records are merged into a single database, resolving
duplicates and different formatting between sources. The records are
ordered according to the frequency of the positive query terms (e.g.,
not preceded by a \(NOT\) modifier) in the title and abstract (``simple
query ordering'').\\
The researcher is then asked to label a number of records to create the
``initial training set'' needed to start the automatic classification.
We suggest manually labelling the first 250 records (see
``hyperparameter optimization'' later). The simple query ordering
increases the positivity rate in the initial training set (Wallace,
Small, et al. 2010), which provide higher sensitivity during automatic
classification (Chawla, Japkowicz, and Kotcz 2004).

@@

The collected citation data have a number of fields characterising a
scientific publication. The framework models the relevance of a record
based on the following fields: title, abstract, authors, keywords, MESH
terms (Lipscomb 2000). A series of Natural Language Processing (NLP)
techniques (Baeza-Yates, Ribeiro-Neto, et al. 1999; Marshall and Wallace
2019; Ananiadou and McNaught 2006) are employed to transform the textual
information in these fields into features for machine learning through a
bag-of-words approach (Marshall and Wallace 2019). The processing of
free text fields (title, abstract) includes: tokenization (i.e.,
extracting the terms), common stopwords (i.e., sentence components
bringing no meaning) removal, part-of-speech filtering (only nouns,
adjectives, verbs and untagged terms are retained), and lemmatization of
the terms (i.e., reduction to their base grammar form). Text processing
for authors, keywords and MESH terms identifies logical units (e.g.,
author's full names, composite keywords) and extracts them.\\
Terms appearing in less than 5\% of the labelled documents are removed
from negative records. All terms in the positive set are kept to
increase sensitivity at the cost of specificity.\\
Some terms tend to co-appear in records (non-consecutive ngrams,
nc-ngrams), often carrying a particular meaning when copresent. To
detect nc-ngrams, we generated a word network representation (Francois
Rousseau 2015) posing edges between terms with a cosine similarity in
terms of record co-occurrence \textgreater{} 0.5. We extracted the
maximal cliques in the network (Eppstein, Löffler, and Strash 2010)
representing highly correlated groups of terms; These groups of terms
are added to the data set as individual features. Only nc-ngrams
comprising a maximum of ten terms are kept.\\
A second network is built using a co-occurrence threshold of 0.9. In
this case, the cliques represent terms that always appear together and
therefore can be considered redundant (i.e., they do not need to be
considered separately). These terms are merged to increase computation
efficiency and reduce overfitting.\\
The output is a Document-Term Matrix (DTM), with \(N_d\) rows
representing the records (\(D_i\)), \(N_t\) terms column for the
\(t_{field}\) terms (divided by record field) and \({0,1}\) values
whether \(t_{field} \in D_i\). We also enriched the DTM with features
referencing the number of terms in each field to help the model scale
term importance based on the field length.

@@

To assign the labels, we employed an ``active learning'' Miwa et al.
(2014) approach, where a human reviews a specific subset of predictions
made from the machine, which is then retrained on the manually reviewed
data set. This process proceeds iteratively, decreasing prediction
uncertainty.\\
Label assignment is done through the identification of an ``uncertainty
zone'' whose construction is possible thanks to the Bayesian nature of
BART, which provides full PPDs instead of point-wise predictions for
each record.\\
To describe the process formally, we define

@@

\hypertarget{relevant-term-extraction}{%
\subsection{Relevant term extraction}\label{relevant-term-extraction}}

@@

Since the algorithm is data-driven, it creates queries that effectively
select positive records from the input data set but may be not specific
enough once applied to actual research databases. Therefore we appended
an extra subquery in \(AND\), which specifies the general topics of our
search and delimitates the search domain.\\
The new query was used to initiate a second search session.

@@

We trained a simple Bayesian logistic regression (surrogate model) on
the reviewed records to evaluate the classification model consistency
(see Discussion for the theoretical justification). The surrogate model
uses as predictor the lower bound of the 98\% PrI of the records' PPD
with weakly regularizing, robust priors for the intercept (Student T
with \(\nu=3,\mu=0,\sigma=2.5\)) and the linear coefficient (Student T
with \(\nu=3,\mu=0,\sigma=1.5\)).\\
The quality of the model was evaluated through Bayesian \(R^2\) (Gelman
et al. 2019), of which we reported the posterior median and 90\%
Credible Interval {[}90\% CrI{]}. The \(R^2\) also provides an
evaluation of the consistency of the original classification model.
Given that this model is conditional only on the BART predictions and
not on the DTM, it is characterized by more uncertainty, providing
plausible worst-case scenarios.\\
The surrogate model is then used to generate the predictive cumulative
distribution of the number of total positive records in the whole data
set. This distribution allows estimating the expected total posterior
``Sensitivity'' and ``Efficiency'' of the classification model in the
full (unreviewed) data set. Efficiency is summarised by the ``Work saved
over random'' (WSoR) statistic: one minus the ratio between the number
of record manually reviewed and those that would be required to find the
same number of positives if classification was performed choosing
records randomly; this last quantity is estimated through a negative
hypergeometric distribution (Chae 1993) over the predicted amount of
positive records.\\
For the number of predicted positive records, the sensitivity and the
efficiency, we reported the ``truncated 90\% PrI'' {[}trunc. 90\%
PrI{]}, which is the uncertainty interval bounded at the number of
observed total positive records (i.e., there cannot be less predicted
positive records than observed).

@@

To evaluate the hyperparameter effect of performance, we set up a ``grid
search'' (Claesen and De Moor 2015; L. Yang and Shami 2020) on a
prelabelled ``validation set'' made of the first 1200 records from the
first session data set. The framework tested each hyperparameter
combination until four CR iterations with no positive records were
returned or the whole data set got labelled.\\
For each combination, a performance score was computed as the product of
``Efficiency'' (1 minus the ratio of records that required review over
the total) and ``Sensitivity'' (number of positive records found over
the total of positives). We then identified homogeneous ``performance
clusters'' of scores given hyperparameter values using a partition tree
(Therneau and Atkinson 2019). For the rest of the study, we used the
best hyperparameter set in terms of Sensitivity followed by Efficiency
from the cluster with the highest average score.

@@

The initial search query for the example topic was:\\

@@

The first search session returned a total of 27600 unique records,
specifically 12719 (71.6\% of the total) records from the EMBASE
database, followed by 9546 (53.8\%) from Pubmed, 3175 (17.9\%) from
SCOPUS, 2100 (11.8\%) from WOS, and 60 (0.34\%) from IEEE (Table 1).
There were various degrees of overlapping between sources, with the
38.4\% of records being present in more than one database and EMBASE and
IEEE being the databases with the higher uniqueness ratios. The final
data set was composed by 17755 unique records.\\
The first 250 records (based on ``simple query ordering'') were manually
labeled. Of these 43 (17.2\%) were labeled as positive, and 207 (82.8\%)
as negative.

@@

\caption{\label{tab:Table 1}\textbf{Table 1}. Distribution of retrieved records by source and session. For each source it is reported the number of records, percentage over the session total (after removing duplicates)' and, number or records specific for a source as absolute value and as percentage over the source total. All session shows records after joining and deduplication of the Session 1 and Session 2 data set.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrlrl}
\toprule
Session & Source & Records & \% over total & Source specific records & \% over source total\\
\midrule
\cellcolor{gray!6}{Session1} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{17755} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 12719 & 71.6\% & 6683 & 52.5\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{9546} & \cellcolor{gray!6}{53.8\%} & \cellcolor{gray!6}{3457} & \cellcolor{gray!6}{36.2\%}\\
 & Scopus & 3175 & 17.9\% & 298 & 9.39\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{2100} & \cellcolor{gray!6}{11.8\%} & \cellcolor{gray!6}{473} & \cellcolor{gray!6}{22.5\%}\\
\addlinespace
 & IEEE & 60 & 0.34\% & 29 & 48.3\%\\
\cellcolor{gray!6}{Session2} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{82579} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 48396 & 58.6\% & 40826 & 84.4\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{28811} & \cellcolor{gray!6}{34.9\%} & \cellcolor{gray!6}{18021} & \cellcolor{gray!6}{62.5\%}\\
 & Scopus & 17070 & 20.7\% & 4908 & 28.8\%\\
\addlinespace
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{12956} & \cellcolor{gray!6}{15.7\%} & \cellcolor{gray!6}{2817} & \cellcolor{gray!6}{21.7\%}\\
 & IEEE & 61 & 0.074\% & 22 & 36.1\%\\
\cellcolor{gray!6}{All Sessions} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{98371} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 59604 & 60.6\% & 46942 & 78.8\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{37278} & \cellcolor{gray!6}{37.9\%} & \cellcolor{gray!6}{21371} & \cellcolor{gray!6}{57.3\%}\\
\addlinespace
 & Scopus & 19353 & 19.7\% & 5181 & 26.8\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{14367} & \cellcolor{gray!6}{14.6\%} & \cellcolor{gray!6}{3175} & \cellcolor{gray!6}{22.1\%}\\
 & IEEE & 108 & 0.11\% & 48 & 44.4\%\\
\bottomrule
\end{tabular}}
\end{table}

@@

The ``\&'' indicates nc-ngrams, i.e., terms strongly co-occurrent in the
documents.\\
The engine was able to pick up the central concept of the research,
i.e., ``patient transport'' or ``transfer'' through a ``network'' of
``facility''ies that facilitates the ``spread'' of infections, and even
one of the authors of this study (Donker T.) as well as the region of
interest (``Orange County'') of another research group active on the
topic of healthcare asociated pathogen spreading over hospital networks.
It is interesting to see that some terms were considered highly relevant
for the BART models (e.g., ``Worker'' in 6th position out of more than
3800 terms considered) although in a simpler linear model their effect
would be hardly significant (statistic: -1.21 s.e.); these are terms
which are relevant only together with other terms but not by themselves,
highlighting the extra predictive power brought by a non-linear model
like BART.\\
A more extensive set of terms is presented in Table 1 of Supplemental
Material S2.

@@

\caption{\label{tab:Table 3}\textbf{Table 3}. Estimated performance summary. The table reports for each session, the number of reviewed records and the percentage over the total. Also, the posterior expected number of positive records, "Sensitivity" and "Efficiency" (as WSoR) are reported, with their 90\% PrI truncated to the observed realization in the dataset [trunc. PrI] (see. methods). Finally the median Bayesian $R^2$ [90\% CrI] of the logistic models is reported. PrI: Predictive Intervals; CrI: Credibility Intervals}
\centering
\begin{tabular}[t]{lll}
\toprule
Indicator & Session 1 & Session 2\\
\midrule
\cellcolor{gray!6}{Total records} & \cellcolor{gray!6}{17755} & \cellcolor{gray!6}{98371}\\
Reviewed records (\% over total records) & 761 (4.29\%) & 1316 (1.34\%)\\
\cellcolor{gray!6}{Expected efficiency (over random) [trunc. 90\% PrI]} & \cellcolor{gray!6}{95.7\% [95.3\%, 95.7\%]} & \cellcolor{gray!6}{98.6\% [98.2\%, 98.7\%]}\\
Observed positive matches (\% over total records) & 101 (0.57\%) & 107 (0.11\%)\\
\cellcolor{gray!6}{Predicted positive matches [trunc. 90\% PrI]} & \cellcolor{gray!6}{101 [101, 108]} & \cellcolor{gray!6}{110 [107, 145]}\\
\addlinespace
Expected sensitivity [trunc. 90\% PrI] & 100\% [93.5\%, 100\%] & 97.3\% [73.8\%, 100\%]\\
\cellcolor{gray!6}{Simple Model $R^2$ [90\% CrI]} & \cellcolor{gray!6}{98.1\% [97.4\%, 98.3\%]} & \cellcolor{gray!6}{98.2\% [97.6\%, 98.3\%]}\\
\bottomrule
\end{tabular}
\end{table}
